### 2019-12-31 docs/thesis-project/article.tex
Update article.tex

\subsection{Structured Overlays}
Structured overlay ensures peer placement follows rigid rules in order to speed up lookup operations, commonly using Distributed Hash Tables or Tree implementations. However, for this reason, these overlays also have higher maintenance costs due to churn, making them less ideal for highly dynamic environments.

\subsubsection{Kademlia} \cite{kademlia} is fully decentralized and designed for key-value storage systems, which, according to the authors, combines provable consistency, performance, latency-minimizing routing, and symmetric topology. Kademlia peer-identifiers and data-keys are built as in Chord\cite{chord}, using consistent hashing. Inserts and lookups on the overlay are unidirectional, according to the distance between two identifiers, calculated using XOR. The unidirectionality allows caching to be done along lookup paths, alleviating hot spots. Each peer in the overlay maintains a binary tree, routing table, whose leaves are lists of peers, called k-buckets, at distances $2^{x}$ to $2^{x+1}$, $x \in\hspace{1mm}\mathclose[0,160\mathclose]$ from itself, sorted according to a least recently seen policy. As a peer receives messages if the sender is a new acquaintance, that sender is placed on the proper k-bucket if there is enough space in it; otherwise, it will replace the least seen peer only if that peer fails to respond to a ping. By preferring old acquaintances, Kademlia seeks to enhance the stability of the overlay based on the observation that the longer a peer remains connected to the network, the higher the probability that it will remain connected at least another hour\cite{ssaroiu:msp2pfss}. This policy also prevents some denial of service attacks, where an enemy floods the network with new peers. The XOR metric gives Kademlia an advantage over other DHT-based implementations by making routing tables less rigid and by allowing peers in the network to learn useful routing information from discovery and lookup messages. Because of the existence of k-buckets, routing can also be done around failed nodes, providing some resistance to churn and partitioning.

The standard Kademlia implementation, however, does not implement an effective mechanism to keep dated entries out of a peer's k-buckets, meaning that the longer a peer stays offline, the worse is k-buckets are. Dated entries removed when the peer contacts a peer and obtains no response, meaning that insert and lookup operations may take longer than they could. The take-away from Kademlia protocol is that both the liveness and the freshness of an overlay can be improved by passively or actively making peers monitor each other.\newline

>>>>

\subsection{Structured Overlays}
Structured overlay ensures peer placement follows rigid rules in order to speed up lookup operations, commonly using Distributed Hash Tables (DHT) or Tree implementations. However, for this reason, these overlays also have higher maintenance costs, making them less ideal for highly dynamic environments.

\subsubsection{Kademlia} \cite{kademlia} is fully decentralized and designed for key-value storage systems, and according to the authors, combines provable consistency, performance, latency-minimizing routing, and symmetric topology. Kademlia peer-identifiers and data-keys are built as in Chord\cite{chord}, using consistent hashing. Inserts and lookups on the overlay are unidirectional, according to the distance between two identifiers, calculated using XOR. The unidirectionality allows caching to be done along lookup paths, alleviating hot spots. Each peer in the overlay maintains a binary tree, routing table, whose leaves are lists of peers, called k-buckets, at distances $2^{x}$ to $2^{x+1}$, $x \in\hspace{1mm}\mathclose[0,160\mathclose]$ from itself, sorted according to the least recently seen policy. As a peer receives messages, if the sender is a new acquaintance, that sender is placed on the proper k-bucket. If a replacement is required, then the least seen peer will be evicted, but only if that peer fails to respond to a ping. This policy helps in the defense against attacks where malicious entities flood the network with new dummy peers. By preferring old acquaintances, Kademlia seeks to enhance the stability of the overlay based on the observation that the longer a peer remains connected to the network, the higher the probability that it will remain connected at least another hour\cite{ssaroiu:msp2pfss}. The XOR metric gives Kademlia an advantage over other DHT-based implementations by making routing tables less rigid and by allowing peers to learn useful routing information from messages they receive. K-buckets allow routing to be done around failed nodes, providing increased churn resistance. We note that Kademlia does not implement an effective mechanism to keep dated entries out of a peer's k-buckets, meaning that the longer a peer stays offline, the worse is k-buckets are when he returns. The standard implementation only removes dated entries when the peer contacts another and obtains no response; While our proposed solution differs from Kademlia's solution, but it raises awareness to the fact that our networks rely upon active peers, while not keeping new interested peers locked out of the system.
